What makes listeners infer teaching intentions?

### 2022-02-02 paper/manuscript.tex
update stats values
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right).

The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; \emph{p} \textless{} 0.001, Piano; \emph{p} \textless{} 0.001). Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = .15, \emph{p} = 0.31, Piano; \emph{r(46)} = -.12, \emph{p} = 0.43).

@@

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left).

The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (;\emph{p} = 0.002). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = .03, \emph{p} = 0.84).

@@

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left).

The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (;\emph{p} = 0.007). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato). The result of the regression indicated that the model explained 64.63 \% of the variance (\emph{F}(4, 43) = 22.50, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.78, \emph{p} \textless{} 0.001) and articulation for the legato parts (KOT; \emph{\(\beta\)} = 0.26, \emph{p} = 0.004) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato). The result of the regression indicated that the model explained 63.97 \% of the variance (\emph{F}(4, 43) = 21.90, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = 0.002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = 0.020) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano). The result of the regression indicated that the model explained 35.90 \% of the variance (\emph{F}(4, 43) = 7.60, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = 0.007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = 0.048) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte). The result of the regression indicated that the model explained 51.21 \% of the variance (\emph{F}(4, 43) = 13.30, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.38, \emph{p} \textless{} 0.001) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 0.99, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.

@@

Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r(34)} = .25, \emph{p} = 0.147, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.019, \emph{Figure \ref{fig:ioi-2}}).

The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091).

@@

Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = 0.390, Staccato; \emph{r(34)} = -.15, \emph{p} = 0.390, \emph{Figure \ref{fig:kot-2}}, left).

For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52). However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.03), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right). Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.

The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; \emph{p} = 0.048, Piano' \emph{p} = 0.004). Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r(34)} = .43, \emph{p} = 0.010) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.01) were more likely to be judged as teaching.

@@

The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .59, \emph{p} \textless{} 0.001).

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato). The result of the regression indicated that the model explained 19.77 \% of the variance (\emph{F}(4, 31) = 3.20, \emph{p} = 0.03). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = 0.011), dynamics (KV) and dynamics contrast (KV-Diff) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching. However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = 0.466) for the legato parts was not a significant predictor as opposed to Experiment 1.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato). The overall was not statistically significant (\(R^{2}\) = 12.28, \emph{F}(4, 31) = 2.20, \emph{p} = 0.09).

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano). The result of the regression indicated that the model explained 60.69 \% of the variance (\emph{F}(4, 31) = 14.50, \emph{p} \textless{} 0.001). It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte). The result of the regression indicated that the model explained 49.49 \% of the variance (\emph{F}(4, 31) = 9.60, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = 0.022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.

>>>>

For dynamics recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = -.04, \emph{p} = 0.81, Piano; \emph{r(46)} = -.19, \emph{p} = 0.19, \emph{Figure \ref{fig:kot-1}}, right). The Shapiro-Wilk normality test revealed that the distribution of KOT for dynamics recordings was not normally distributed (Forte; \emph{p} \textless{} 0.001, Piano; \emph{p} \textless{} 0.001). Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values and participants' judgments as teaching (Forte; \emph{r(46)} = .15, \emph{p} = 0.31, Piano; \emph{r(46)} = -.12, \emph{p} = 0.43).

@@

For articulation recordings, there was no significant relationship between KV values and participants' judgments as teaching (Legato; \emph{r(46)} = .10, \emph{p} = 0.52, Staccato; \emph{r(46)} = -.02, \emph{p} = 0.87, \emph{Figure \ref{fig:vel-1}}, left). The Shapiro-Wilk normality test revealed that the distribution of KOT for articulation recordings for legato was not normally distributed (\emph{p} = 0.002). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = .03, \emph{p} = 0.84).

@@

For articulation recordings, there was no significant relationship between KV difference between legato and staccato and participants' judgments as teaching (From Legato to Staccato; \emph{r(46)} = -.26, \emph{p} = 0.071, From Staccato to Legato; \emph{r(46)} = -.19, \emph{p} = 0.21, \emph{Figure \ref{fig:vel-diff-1}}, left). The Shapiro-Wilk normality test revealed that the distribution of KV difference for articulation recordings for transition points from legato to staccato was not normally distributed (\emph{p} = 0.007). A Spearman's rank correlation coefficients also showed that there was no significant relationship between KOT values for legato and participants' judgments as teaching (\emph{r(46)} = -.23, \emph{p} = 0.12).

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato). The result of the regression indicated that the model explained 64.63 \% of the variance (\emph{F}(4, 43) = 22.5, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.78, \emph{p} \textless{} 0.001) and articulation for the legato parts (KOT; \emph{\(\beta\)} = 0.26, \emph{p} = 0.004) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato). The result of the regression indicated that the model explained 63.97 \% of the variance (\emph{F}(4, 43) = 21.9, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.52, \emph{p} = 0.002) and articulation for the staccato parts (KOT; \emph{\(\beta\)} = -0.28, \emph{p} = 0.020) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano). The result of the regression indicated that the model explained 35.90 \% of the variance (\emph{F}(4, 43) = 7.58, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.35, \emph{p} = 0.007) and dynamics for the forte parts (KV; \emph{\(\beta\)} = 0.73, \emph{p} = 0.048) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte). The result of the regression indicated that the model explained 51.21 \% of the variance (\emph{F}(4, 43) = 13.3, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.38, \emph{p} \textless{} 0.001) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 0.99, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.

@@

Unlike Experiment 1, there was no significant relationship between performance tempi (IOIs) and participants' judgments as teaching for both techniques (Articulation; \emph{r(34)} = .25, \emph{p} = 0.15, Dynamics; \emph{r(34)} = .39, \emph{p} = 0.02, \emph{Figure \ref{fig:ioi-2}}). The Shapiro-Wilk normality test revealed that the distribution of IOIs for dynamics recordings was not normally distributed (\emph{p} = 0.080). A Spearman's rank correlation coefficient also showed that there was no significant relationship between tempi for dynamics performances and participants' judgments as teaching (\emph{r(34)} = .29, \emph{p} = 0.091).

@@

Unlike Experiment 1, for articulation recordings, there was no significant relationship between KOT values and participants' judgments as teaching (Legato; \emph{r(34)} = -.03, \emph{p} = 0.39, Staccato; \emph{r(34)} = -.15, \emph{p} = 0.39, \emph{Figure \ref{fig:kot-2}}, left).

For dynamics recordings, there was no significant relationship between KOT values for forte and participants' judgments as teaching (\emph{r(34)} = -.11, \emph{p} = 0.52). However, there was a significant relationship between KOT values for piano and participants' judgments as teaching (\emph{r(34)} = -.35, \emph{p} = 0.034), suggesting that performances with louder staccato were more likely to be considered as teaching performance (\emph{Figure \ref{fig:kot-2}}, right).

@@

As Experiment 1, for dynamics recordings, there was a significant relationship between KV values and participants' judgments as teaching (\emph{Figure \ref{fig:vel-2}}, right). Specifically, performances with louder forte (\emph{r(34)} = .45, \emph{p} = 0.007) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.006) were more likely to be judged as teaching. The Shapiro-Wilk normality test revealed that the distribution of KV values for dynamics recordings was not normally distributed (Forte; \emph{p} = 0.048, Piano' \emph{p} = 0.004). Spearman's rank correlation coefficient also confirmed that performances with louder forte (\emph{r(34)} = .43, \emph{p} = 0.010) and softer piano (\emph{r(34)} = -.45, \emph{p} = 0.013) were more likely to be judged as teaching.

@@

The Shapiro-Wilk normality test revealed that the distribution of KV-Diff values for dynamics recordings was not normally distributed (Forte to Piano; \emph{p} = 0.850, Piano to Forte; \emph{p} = 0.008). Spearman's rank correlation coefficient also confirmed that performances with larger contrasts between forte and piano were more likely to be judged as teaching (Forte to Piano; \emph{r(34)} = -.73, \emph{p} \textless{} 0.001, Piano to Forte; \emph{r(34)} = .57, \emph{p} \textless{} 0.001).

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for legato parts), dynamics (KV for legato parts) and dynamics contrast (KV-Diff from legato to staccato). The result of the regression indicated that the model explained 19.77 \% of the variance (\emph{F}(4, 31) = 3.16, \emph{p} = 0.028). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.58, \emph{p} = 0.011), dynamics (KV; \emph{\(\beta\)} = 1.10, \emph{p} = 0.018) and dynamics contrast (KV-Diff; \emph{\(\beta\)} = 1.90, \emph{p} = 0.006) for the legato parts were articulation for the legato parts were significant predictors of participants' judgments as teaching. However, articulation (KOT; \emph{\(\beta\)} = -0.08, \emph{p} = 0.47) for the legato parts was not a significant predictor as opposed to Experiment 1.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for staccato parts), dynamics (KV for staccato parts) and dynamics contrast (KV-Diff from staccato to legato). The overall model was not statistically significant (\(R^{2}\) = 12.3, \emph{F}(4, 31) = 2.22, \emph{p} = 0.09).

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for forte parts), dynamics (KV for forte parts) and dynamics contrast (KV-Diff from forte to piano). The result of the regression indicated that the model explained 60.69 \% of the variance (\emph{F}(4, 31) = 14.5, \emph{p} \textless{} 0.001). It was found that dynamics contrast from forte to piano (KV-Diff; \emph{\(\beta\)} = -1.64, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.

@@

A multiple regression analysis was conducted to predict participants' judgments as teaching based on performance features of tempo (IOIs), articulation (KOT for piano parts), dynamics (KV for piano parts) and dynamics contrast (KV-Diff from piano to forte). The result of the regression indicated that the model explained 49.49 \% of the variance (\emph{F}(4, 31) = 9.57, \emph{p} \textless{} 0.001). It was found that tempo (IOIs; \emph{\(\beta\)} = 0.55, \emph{p} = 0.022) and dynamics contrast from piano to forte (KV-Diff; \emph{\(\beta\)} = 1.09, \emph{p} \textless{} 0.001) were significant predictors of participants' judgments as teaching.
